Lightweight Ruby Framework\\ for Improving Embedded Software Efficiency

### 2016-10-20 jssst/paper.tex
adjust

%
% File: thesis.tex
% Created: 月 11 30 08:00 午後 2015 東京 (標準時)
% Last Change: 月 11 30 08:00 午後 2015 東京 (標準時)
%
\input{dummy/dummy.tex}
\documentclass{sig-alternate-05-2015}
%\usepackage[dvipdfmx]{graphicx}
\usepackage{amssymb}
\usepackage{enumerate,cite,url}
\usepackage{listings,jlisting}
\lstset{%
    language={c},%
    basicstyle={\small},%
    identifierstyle={\small},%
    commentstyle={\small\itshape},%
    keywordstyle={\small},%\bfseries},%
    ndkeywordstyle={\small},%
    stringstyle={\small\it},
    frame={tb},
    breaklines=true,
    columns=[l]{fullflexible},%
    numbers=left,%
    xrightmargin=0zw,%
    xleftmargin=3zw,%
    numberstyle={\scriptsize},%
    stepnumber=1,
    numbersep=1zw,%
    %lineskip=-0.5ex%
}

% Copyright
\setcopyright{acmcopyright}
% DOI
\doi{10.475/123_4}
% ISBN
\isbn{123-4567-24-567/08/06}
%Conference
\conferenceinfo{EMSOFT '16}{October 2--7, 2016, Pittsburgh, USA}
\acmPrice{\$15.00}

\title{Bluetooth Loader for mruby Bytecode \\ in Multiple Virtual Machine Environment}
\numberofauthors{3}
% \author{
% \alignauthor
% Takuro Yamamoto\\
%     \affaddr{Graduate School of Engineering Science, Osaka University}\\
%     \affaddr{Osaka, JAPAN}\\
%        % \affaddr{Wallamaloo, New Zealand}\\
%        % \email{trovato@corporation.com}
% \alignauthor
% Hiroshi Oyama\\
%     \affaddr{OKUMA Corporation}\\
%     \affaddr{Aichi, JAPAN}\\
%        % \affaddr{Dublin, Ohio 43017-6221}\\
%        % \email{webmaster@marysville-ohio.com}
% \alignauthor
% Takuya Azumi\\
%     \affaddr{Graduate School of Engineering Science, Osaka University}\\
%     \affaddr{Osaka, JAPAN}\\
%        % \affaddr{Hekla, Iceland}\\
%        % \email{larst@affiliation.org}
% }
%\author{Takuro Yamamoto}
%\date{\today}

\begin{document}
\maketitle
\begin{abstract}
Recently, the productivity of embedded systems has become problematic due to their increasing complexity and scale.
To improve the productivity, the mruby on TOPPERS embedded component system (TECS) framework, which employs mruby (i.e., lightweight Ruby) and supports component-based development, has been proposed.
In the current mruby on TECS framework, mruby programs must be compiled and linked every time they are modified, because mruby bytecode are incorporated in the platform.
Moreover, while the framework supports multiple virtual machines (VMs), developers must be familiar with the functions of real-time operating systems to effectively execute multiple mruby programs concurrently or in parallel.
To improve development efficiency, we propose a Bluetooth loader for mruby bytecode as an extension of mruby on TECS.
The loader executes two mruby bytecodes, i.e., the mruby application bytecode and mruby library bytecode.
The mruby application bytecode is modified frequently and sent from a host to a target device by the developers, while the mruby library bytecode is modified infrequently and preserved beforehand on a storage/ROM device during the first compilation.
In addition, multiple mruby programs can run cooperatively in the proposed framework.
Compared to mruby on TECS, the RiteVM scheduler simplifies multitasking.
Synchronization of initializing multiple tasks is also implemented using an Eventflag. 
Experimental results demonstrate the advantages of the proposed framework.
\end{abstract}

\keywords{embedded software; scripting language; component-based development}
\section{Introduction}
Currently, embedded systems, e.g., Internet of Things applications, must demonstrate high quality and high performance.
This requirement has led to an increase in their complexity and scale; moreover, these systems need to have low production costs and short development cycles.

@@

{\mybf Contributions}: The proposed framework provides the following contributions:
\begin{enumerate}
\item {\mybf Improved software development efficiency.}
Developers do not need to rewrite a storage/ROM device and restart an RTOS.
The Bluetooth loader supports continuous loading, which reduces Bluetooth set-up time (i.e., pairing).
\item {\mybf Execution of multiple mruby programs concurrently or in parallel.}
Developers can implement multiple tasks without RTOS knowledge because the RiteVM scheduler switches tasks cyclically.
\item {\mybf Synchronized execution of multiple RiteVM tasks.}
The proposed framework synchronizes multiple RiteVM tasks (i.e., mruby applications).
\item {\mybf Benefits of CBD:}
The paper focuses on the benefits of CBD and provides specific examples.
\end{enumerate}

{\mybf Organization}: The reminder of this paper is organized as follows.
Section \ref{sec:Background} introduces the basic technologies, i.e., mruby, TECS, and mruby on TECS.
Section \ref{sec:Design and Implementation} describes the design and implementation of the proposed framework.
Section \ref{sec:Evaluation} evaluates the proposed framework.
Related work is discussed in Section \ref{sec:Related work}.
Conclusions and suggestions for future work are presented in Section \ref{sec:Conclusion}.

\begin{figure}[t]
    \centering
    \includegraphics[width=8.6cm,clip]{figure/proposed.eps}
    \vspace{0.5mm}
    \caption{System model of the proposed framework}
    \vspace{1mm}
    \label{fig:proposed}
\end{figure}

@@

mruby, which retains the usability and readability of Ruby, requires fewer resources, and thus, is suitable for embedded systems.
In addition, mruby includes a VM mechanism, and thus, mruby programs can run on any operating system as long as a VM is implemented.
The mruby/RiteVM mechanism is shown in Figure \ref{fig:mruby}.
The mruby compiler translates an mruby code into a bytecode, which can be interpreted by a RiteVM; thus, mruby programs can be executed on any target device with a RiteVM.
\begin{figure}[t]
    \centering
    \includegraphics[width=8.6cm,clip]{figure/mruby.eps}
    \vspace{0.5mm}
    \caption{mruby/RiteVM mechanism}
    \vspace{1mm}
    \label{fig:mruby}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8.6cm,clip]{figure/component_diagram.eps}
    % \vspace{0.5mm}
    \caption{Component Diagram}
    \vspace{1mm}
    \label{fig:component}
\end{figure}

\subsubsection{Component Model}
Figure \ref{fig:component} shows a component diagram.
A {\myit cell}, which is an instance of a component in TECS, consists of {\myit entry} ports, {\myit call} ports, attributes and internal variables.
An {\myit entry} port is an interface that provides functions to other {\myit cell}s, and a {\myit call} port is an interface that enables the use of other {\myit cell}'s functions.
A {\myit cell} has one or more {\myit entry} ports and {\myit call} ports.
{\myit Cell} functions are implemented in C.

The type of {\myit entry}/{\myit call} port is defined by a {\myit signature}, which is a set of functions.
A {\myit signature} is the interface definition of a {\myit cell}.
The {\myit cell}'s  {\myit call} port can be connected to the {\myit entry} port of another {\myit cell} by the same {\myit signature}.
Here, {\myit celltype} defines one or more {\myit call}/{\myit entry} ports, attributes, and internal variables of a {\myit cell}.

\subsubsection{Component Description}
In TECS, components are described by {\myit signature}, {\myit celltype}, and build written in component description language (CDL).
% TECS code is written in CDL (component description language) file.
These components are described as follows.

\begin{description}
    \item[{\mybf Signature Description}]\mbox{}\\
        The {\myit signature} defines a {\myit cell} interface.
        The {\myit signature} name follows the keyword {\myit signature} and takes the prefix ``s'' e.g., sMotor (Figure \ref{signature}).
        In TECS, to clarify the function of an interface, specifiers such as [in] and [out] are used, which represent input and output, respectively.
\begin{figure}[t]
\centering
\begin{lstlisting}
signature sMotor {
    int32_t getCounts( void );
    ER resetCounts( void );
    ER setPower( [in]int power );
    ER stop( [in] bool_t brake );
    ER rotate( [in] int degrees, [in] uint32_t speed_abs,
              [in] bool_t blocking );
    void initializePort( [in]int32_t type );
};
\end{lstlisting}
\vspace{1mm}
\caption{Signature Description}
\vspace{1mm}
\label{signature}
\end{figure}
    \item[{\mybf Celltype Description}]\mbox{}\\
        The {\myit celltype} defines {\myit entry} ports, {\myit call} ports, attributes, and variables.
        A {\myit celltype} name with the prefix ``t'' follows the keyword {\myit celltype}, e.g., tCaller (Figure \ref{celltype}).
        To define {\myit entry} ports, a {\myit signature}, e.g., sMotor, and an {\myit entry} port name, e.g., eMotor, follow the keyword {\myit entry}.
        {\myit Call} ports are defined similarly.
        Attributes and variables follow the keywords {\myit attr} and {\myit var}, respectively.
\begin{figure}[t]
\centering
\begin{lstlisting}
celltype tCaller {
    call sMotor cMotor;
};
celltype tMotor {
    entry sMotor eMotor;
    attr {
        int32_t port;
    };
    var {
        int32_t currentSpeed = 0;
    };
};
\end{lstlisting}
\vspace{1mm}
\caption{Celltype Description}
\vspace{1mm}
\label{celltype}
\end{figure}
    \item[{\mybf Build Description}]\mbox{}\\
        The build description is used to instantiate and connect {\myit cell}s.
        Figure \ref{build} shows an example of a build description.
        A {\myit celltype} name and {\myit cell} name, e.g., tMotor and Motor, respectively, follow the keyword {\myit cell}.
        To compose {\myit cell}s, a {\myit call} port, {\myit cell}'s name, and an {\myit entry} port are described in that order.
        In Figure \ref{build}, {\myit entry} port eMotor in {\myit cell} Motor is connected to {\myit call} port cMotor in {\myit cell} Caller.
        {\myit C\_EXP} calls macros defined in C files.

\begin{figure}[t]
\centering
\begin{lstlisting}
cell tMotor Motor {
    port = C_EXP("PORT_A");
};
cell tCaller Caller {
    cMotor = Motor.eMotor;
};
\end{lstlisting}
\vspace{1mm}
\caption{Build Description}
\vspace{1mm}
\label{build}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8.6cm,clip]{figure/mrubyontecs.eps}
    \vspace{0.5mm}
\caption{System model of existing mruby on TECS}
    \vspace{1mm}
\label{fig:mrubyontecs}
\end{figure}

@@

Figure \ref{fig:mruby_TECS_bridge} illustrates an mruby-TECS bridge used to control a motor.
The left side of BridgeMotor belongs to the mruby program.
The right side of BridgeMotor belongs to TECS component.
\begin{figure}[t]
    \centering
    \includegraphics[width=8.6cm,clip]{figure/mruby_TECS_bridge.eps}
    \vspace{0.5mm}
\caption{mruby-TECS bridge}
    \vspace{1mm}
\label{fig:mruby_TECS_bridge}
\end{figure}

The mruby-TECS bridge generates a {\myit celltype}, which is called from the mruby code, and an mruby class, which corresponds to a developer-specified TECS component to invoke a C function from the mruby program.

The generated mruby-TECS bridge supports registration of classes and methods for mruby.
Methods in an mruby class are defined by generation codes for an mruby-TECS bridge, such as setPower and stop.
Thus, when a method is called in an mruby program, the mruby-TECS bridge calls the function defined in the TECS component such as a Motor {\myit cell}.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8.6cm,clip]{figure/system_model.eps}
    \vspace{0.5mm}
\caption{Detailed system model of the proposed framework}
    \vspace{1mm}
\label{fig:system_model}
\end{figure}

@@

\subsubsection{RiteVM Component with Bluetooth Loader for mruby Bytecode}
\begin{figure}[t]
    \centering
    \includegraphics[width=8.6cm,clip]{figure/component_bluetooth.eps}
    \vspace{0.5mm}
\caption{Component diagram of Bluetooth loader for mruby bytecode}
    \vspace{1mm}
\label{fig:component_bluetooth}
\end{figure}
The proposed framework provides a RiteVM with a Bluetooth loader for mruby bytecode as a TECS component.
This component is an extension of the RiteVM component described in \cite{par:mrubyonTECS}.
It receives bytecodes via Bluetooth and manages the RiteVM configuration, such as generating mruby library bytecodes automatically.
This generated bytecode is prepared beforehand on the storage/ROM device and differs from the bytecode transferred with Bluetooth.

Figure \ref{fig:component_bluetooth} shows a component diagram of MrubyTask1 and RiteVMBluetooth1 {\myit cell}s.
The MrubyTask1 {\myit cell} is a componentized task of the RTOS (TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs}).
The RiteVMBluetooth1 {\myit cell} is the RiteVM component with the Bluetooth loader for mruby bytecode.
Bytecode on the host is transferred and received.
In this framework, ZMODEM \cite{par:zmodem} is used as the binary transfer protocol.

\begin{figure}[t]
    \centering
    \includegraphics[width=8.6cm,clip]{figure/control_flow.eps}
    \vspace{0.5mm}
\caption{Process flow of Bluetooth loader for mruby bytecode}
    \vspace{1mm}
\label{fig:control_flow}
\end{figure}

\begin{figure}[t]
\centering
\begin{lstlisting}
/* tRiteVMBluetooth.cdl */
celltype tRiteVMBluetooth1 {
    entry sTaskBody eMrubyBody;
    [optional] call sEventflag cEventflag[];
    [optional] call sSemaphore cSemaphore;
    attr {
      [omit]char_t *mrubyLib;
      char_t *irepLib = 
                    C_EXP("&$cell_global$_irep");
      uint32_t irepAppSize = 
                    C_EXP( BUFFER_SIZE );
      FLGPTN setptn;
    };
    var {
        mrb_state *mrb;
        mrbc_context *context;
        [size_is(irepAppSize)] uint8_t *irepApp;
    };
};
\end{lstlisting}
\vspace{1mm}
\caption{Celltype description for RiteVM with Bluetooth loader for mruby bytecode}
\vspace{1mm}
\label{celltype_mrubybluetooth}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=8.6cm,clip]{figure/rotateReadyQueue.eps}
    \vspace{0.5mm}
\caption{RiteVM scheduler design}
    \vspace{1mm}
\label{fig:rotateReadyQueue}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=8.6cm,clip]{figure/cyclic_handler.eps}
    % \vspace{0.5mm}
\caption{Component diagram of RiteVM scheduler}
    \vspace{1mm}
\label{fig:cyclic_handler}
\end{figure}

@@

composite tRiteVMScheduler {
    attr {
        ATR    attribute      = C_EXP("TA_NULL");
        RELTIM cyclicTime  = 1;
        RELTIM cyclicPhase = 1;
        PRI    priority;
    };
    cell tRiteVMSchedulerMain RiteVMSchedulerMain {
        priority = composite.priority;
    };
    cell tCyclicHandler CyclicHandler {
        ciBody      = RiteVMSchedulerMain.eiBody;
        attribute   = composite.attribute;
        cyclicTime  = composite.cyclicTime;
        cyclicPhase = composite.cyclicPhase;
    };
};
    \end{lstlisting}
    \vspace{1mm}
\caption{Celltype description of RiteVM scheduler}
    \vspace{1mm}
\label{celltype_cyclic_handler}
\end{figure}
\begin{figure}[t]
    \centering
    \begin{lstlisting}
cell tRiteVMScheduler RiteVMScheduler {
    attribute   = C_EXP("TA_STA");
    cyclicTime  = 1;
    cyclicPhase = 1;
    priority    =
        C_EXP("RITEVM_PRIORITY");
};
\end{lstlisting}
    \vspace{1mm}
\caption{Build description of RiteVM scheduler}
    \vspace{1mm}
\label{build_cyclic_handler}
\end{figure}

@@

Figure \ref{fig:cyclic_handler} shows a component diagram of the RiteVM scheduler.
The RiteVM scheduler consists of CyclicHandler and RiteVMSchedulerMain.
The CyclicHandler {\myit cell} configures the periodic handler based on $\mu$ITRON.
Cyclic handlers based on $\mu$ITRON are described in the literature \cite{par:microITRON}.
The CyclicHandler {\myit cell} has the attributes of the {\myit cell}.
The RiteVMSchedulerMain {\myit cell} processes the body of a periodic handler.
Note that {\myit rotateReadyQueue} is implemented as the body.
Figure \ref{celltype_cyclic_handler} shows tRiteVMScheduler {\myit celltype}, which is a {\myit composite cell} consisting of two {\myit cell}s.
The {\myit call} port of RiteVMSchedulerMain is connected to the {\myit entry} port of the Kernel {\myit cell} ({\myit tKernel.eiKernel}) to call kernel functions.
The attribute is used as the {\myit rotateReadyQueue} arguments.

Figure \ref{build_cyclic_handler} shows the build description of the RiteVM scheduler.
The RiteVMScheduler {\myit cell} has attributes to configure the scheduler such as attribute, cyclicTime, cyclicPhase, and priority.
In this case, the RiteVM scheduler is executed when it is generated, because the attribute is {\myit TA\_STA}, which indicates that the periodic handler is in an operational state after creation.
Note that the scheduler executes every 1 msec.
RITEVM\_PRIORITY defines the priority of mruby tasks.
In the function of RiteVMSchedulerMain, {\myit rotateReadyQueue} is implemented and the priority is passed as the argument.

\begin{figure}[t]
    \centering
    \includegraphics[width=8.6cm,clip]{figure/Eventflag.eps}
    \vspace{0.5mm}
\caption{Design of Eventflag using TECS (only differences are shown)}
    \vspace{1mm}
\label{fig:Eventflag}
\end{figure}

@@

 \begin{figure}[t]
    \centering
    \includegraphics[width=8.6cm,clip]{figure/eval_synchronization.eps}
    \vspace{0.5mm}
\caption{Synchronization of multiple RiteVM tasks}
    \vspace{1mm}
\label{fig:eval_synchronization}
\end{figure}

>>>>

% Sample file for the use of compsoft style file.
%
\documentclass[S,R,E]{article/compsoft}

% Preamble
%
% 「コンピュータソフトウェア」誌に掲載される論文の場合，次で
% 巻数，号数，開始ページ，終了ページを指定する．
\volNoPp{29}{1}{78}{84}

% ワークショップによる推薦論文の場合，ワークショップ名を指定する．
% \suisen{ワークショップ名}

% 特集の場合，特集のタイトルを与える．
% \tokushu{特集のタイトル}

% 大会論文の場合，¥taikai で開催年を指定する．ここで指定した年から
% 大会の回数は計算される．
% \taikai{2009}

% ここに，使用するパッケージを列挙する．
%\usepackage[dvips]{graphics}
\usepackage[dvipdfmx]{graphicx}
\usepackage{amssymb}
\usepackage{float}
\usepackage{enumerate,cite,url}
\usepackage{listings,jlisting}
\lstset{%
    language={c},%
    basicstyle={\small},%
    identifierstyle={\small},%
    commentstyle={\footnotesize\itshape},%
    keywordstyle={\small},%\bfseries},%
    ndkeywordstyle={\small},%
    stringstyle={\small\it},
    frame={tb},
    breaklines=true,
    columns=[l]{fullflexible},%
    numbers=left,%
    xrightmargin=0zw,%
    xleftmargin=3zw,%
    numberstyle={\scriptsize},%
    stepnumber=1,
    numbersep=1zw,%
    lineskip=-0.5ex%
}

% ユーザが定義したマクロなどはここに置く．ただし学会誌のスタイルの
% 再定義は原則として避けること．

\begin{document}

% 論文のタイトル
\title{Lightweight Ruby Framework\\ for Improving Embedded Software Efficiency}

% 著者
% 和文論文の場合，姓と名の間には半角スペースを入れ，
% 複数の著者の間は全角スペースで区切る
%
\author{Takuro Yamamoto　Hiroshi Oyama　Takuya Azumi}
%
% ここにタイトル英訳 (英文の場合は和訳) を書く．
%
\ejtitle{軽量Rubyを用いた効率的な組込みソフトウェア開発フレームワーク}
%
% ここに著者英文表記 (英文の場合は和文表記) および
% 所属 (和文および英文) を書く．
% 複数著者の所属はまとめてよい．
%
\shozoku{山本　拓朗, 安積　卓也}{大阪大学大学院基礎工学研究科}%
{Graduate School of Engineering Science, Osaka University}
\shozoku{大山　博司}{オークマ株式会社}%
{OKUMA Corporation}

%
% 出典情報は \shutten とすれば出力される．
\shutten
%
% 受付年月日，記事カテゴリなどは自動的に生成される．
\uketsuke{2011}{12}{15}
%
% その他，脚注に入れるものがあれば，¥note に記述する．
%\note{脚注に入れる内容}

%
% 和文アブストラクト
% \Jabstract{%
% 近年，組込みシステムは複雑化・大規模化しているため，ソフトウェアの生産性が問題になっている．
% 組込みソフトウェア開発の生産性の向上を目的として，mruby（軽量Ruby）を適用させたコンポーネントベース開発が可能なフレームワークであるmruby on TECSを提案してきた．
% 現状のmruby on TECSでは，プラットフォームにmrubyバイトコードを組み込んでいるため，mrubyプログラムを修正する度にコンパイル・リンクし直す必要がある．
% さらに，マルチVMを提供しているが，複数のmrubyプログラムを効率良く並行動作させるには開発者がリアルタイムOSの機能を熟知している必要がある．
% 本研究では，mruby on TECSの拡張として，mrubyアプリケーションのバイトコードをBluetoothで転送することで開発効率を向上させる．
% さらに，複数のmrubyプログラムを協調動作できるフレームワークを提案する．
% }
%
% 英文アブストラクト（本サンプルの原論文にはなし）
\Eabstract{
The complexity and scale of embedded software have increased.
To improve the productivity, the mruby on TOPPERS embedded component system (TECS) framework, which employs a scripting language (i.e., lightweight Ruby) and supports component-based development, has been proposed.
In the current mruby on TECS framework, mruby programs must be compiled and linked every time they are modified, because mruby bytecode are incorporated in the platform.
Moreover, while the framework supports multiple virtual machines (VMs), developers must be familiar with the functions of real-time operating systems to effectively execute multiple mruby programs concurrently or in parallel.
This paper proposed an extended mruby on TECS framework that improves development efficiency more than the current framework.
We implemented a Bluetooth loader receives an mruby bytecode, and a RiteVM scheduler simplifies multitasking.
Synchronization of initializing multiple tasks is also implemented using an Eventflag.
Experimental results demonstrate the advantages of the proposed framework.
}
%
\maketitle

%%%%%%%%%%%本文%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}
Currently, embedded systems, e.g., Internet of Things applications, must demonstrate high quality and high performance.
This requirement has led to an increase in their complexity and scale; moreover, these systems need to have low production costs and short development cycles.

@@

{\bf Contributions}: The proposed framework provides the following contributions:
\begin{enumerate}
\item {\bf Improved software development efficiency.}
Developers do not need to rewrite a storage/ROM device and restart an RTOS.
The Bluetooth loader supports continuous loading, which reduces Bluetooth set-up time (i.e., pairing).
\item {\bf Execution of multiple mruby programs concurrently or in parallel.}
Developers can implement multiple tasks without RTOS knowledge because the RiteVM scheduler switches tasks cyclically.
\item {\bf Synchronized execution of multiple RiteVM tasks.}
The proposed framework synchronizes multiple RiteVM tasks (i.e., mruby applications).
\item {\bf Benefits of CBD:}
The paper focuses on the benefits of CBD and provides specific examples.
\end{enumerate}

{\bf Organization}: The reminder of this paper is organized as follows.
Section \ref{sec:Background} introduces the basic technologies, i.e., mruby, TECS, and mruby on TECS.
Section \ref{sec:Design and Implementation} describes the design and implementation of the proposed framework.
Section \ref{sec:Evaluation} evaluates the proposed framework.
Related work is discussed in Section \ref{sec:Related work}.
Conclusions and suggestions for future work are presented in Section \ref{sec:Conclusion}.

\begin{figure*}[t]
    \centering
    \includegraphics[width=14cm,clip]{figure/proposed.eps}
    \caption{System model of the proposed framework}
    \label{fig:proposed}
\end{figure*}

@@

mruby, which retains the usability and readability of Ruby, requires fewer resources, and thus, is suitable for embedded systems.
In addition, mruby includes a VM mechanism, and thus, mruby programs can run on any operating system as long as a VM is implemented.
The mruby/RiteVM mechanism is shown in Figure \ref{fig:mruby}.
The mruby compiler translates an mruby code into a bytecode, which can be interpreted by a RiteVM; thus, mruby programs can be executed on any target device with a RiteVM.
\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/mruby.eps}
    \caption{mruby/RiteVM mechanism}
    \label{fig:mruby}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/component_diagram.eps}
    \caption{Component Diagram}
    \label{fig:component}
\end{figure}

\subsubsection{Component Model}
Figure \ref{fig:component} shows a component diagram.
A {\it cell}, which is an instance of a component in TECS, consists of {\it entry} ports, {\it call} ports, attributes and internal variables.
An {\it entry} port is an interface that provides functions to other {\it cell}s, and a {\it call} port is an interface that enables the use of other {\it cell}'s functions.
A {\it cell} has one or more {\it entry} ports and {\it call} ports.
{\it Cell} functions are implemented in C.

The type of {\it entry}/{\it call} port is defined by a {\it signature}, which is a set of functions.
A {\it signature} is the interface definition of a {\it cell}.
The {\it cell}'s  {\it call} port can be connected to the {\it entry} port of another {\it cell} by the same {\it signature}.
Here, {\it celltype} defines one or more {\it call}/{\it entry} ports, attributes, and internal variables of a {\it cell}.

\subsubsection{Component Description}
In TECS, components are described by {\it signature}, {\it celltype}, and build written in component description language (CDL).
% TECS code is written in CDL (component description language) file.
These components are described as follows.

\begin{description}
    \item[{\bf Signature Description}]\mbox{}\\
        The {\it signature} defines a {\it cell} interface.
        The {\it signature} name follows the keyword {\it signature} and takes the prefix ``s'' e.g., sMotor (Figure \ref{signature}).
        In TECS, to clarify the function of an interface, specifiers such as [in] and [out] are used, which represent input and output, respectively.
\begin{figure}[t]
\centering
\begin{lstlisting}
signature sMotor {
    int32_t getCounts( void );
    ER resetCounts( void );
    ER setPower( [in]int power );
    ER stop( [in] bool_t brake );
    ER rotate( [in] int degrees, [in] uint32_t speed_abs,
              [in] bool_t blocking );
    void initializePort( [in]int32_t type );
};
\end{lstlisting}
\caption{Signature Description}
\label{signature}
\end{figure}
    \item[{\bf Celltype Description}]\mbox{}\\
        The {\it celltype} defines {\it entry} ports, {\it call} ports, attributes, and variables.
        A {\it celltype} name with the prefix ``t'' follows the keyword {\it celltype}, e.g., tCaller (Figure \ref{celltype}).
        To define {\it entry} ports, a {\it signature}, e.g., sMotor, and an {\it entry} port name, e.g., eMotor, follow the keyword {\it entry}.
        {\it Call} ports are defined similarly.
        Attributes and variables follow the keywords {\it attr} and {\it var}, respectively.
\begin{figure}[t]
\centering
\begin{lstlisting}
celltype tCaller {
    call sMotor cMotor;
};
celltype tMotor {
    entry sMotor eMotor;
    attr {
        int32_t port;
    };
    var {
        int32_t currentSpeed = 0;
    };
};
\end{lstlisting}
\caption{Celltype Description}
\label{celltype}
\end{figure}
    \item[{\bf Build Description}]\mbox{}\\
        The build description is used to instantiate and connect {\it cell}s.
        Figure \ref{build} shows an example of a build description.
        A {\it celltype} name and {\it cell} name, e.g., tMotor and Motor, respectively, follow the keyword {\it cell}.
        To compose {\it cell}s, a {\it call} port, {\it cell}'s name, and an {\it entry} port are described in that order.
        In Figure \ref{build}, {\it entry} port eMotor in {\it cell} Motor is connected to {\it call} port cMotor in {\it cell} Caller.
        {\it C\_EXP} calls macros defined in C files.

\begin{figure}[t]
\centering
\begin{lstlisting}
cell tMotor Motor {
    port = C_EXP("PORT_A");
};
cell tCaller Caller {
    cMotor = Motor.eMotor;
};
\end{lstlisting}
\caption{Build Description}
\label{build}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/mrubyontecs.eps}
\caption{System model of existing mruby on TECS}
\label{fig:mrubyontecs}
\end{figure}

@@

Figure \ref{fig:mruby_TECS_bridge} illustrates an mruby-TECS bridge used to control a motor.
The left side of BridgeMotor belongs to the mruby program.
The right side of BridgeMotor belongs to TECS component.
\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/mruby_TECS_bridge.eps}
\caption{mruby-TECS bridge}
\label{fig:mruby_TECS_bridge}
\end{figure}

The mruby-TECS bridge generates a {\it celltype}, which is called from the mruby code, and an mruby class, which corresponds to a developer-specified TECS component to invoke a C function from the mruby program.

The generated mruby-TECS bridge supports registration of classes and methods for mruby.
Methods in an mruby class are defined by generation codes for an mruby-TECS bridge, such as setPower and stop.
Thus, when a method is called in an mruby program, the mruby-TECS bridge calls the function defined in the TECS component such as a Motor {\it cell}.

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/system_model.eps}
\caption{Detailed system model of the proposed framework}
\label{fig:system_model}
\end{figure}

@@

\subsubsection{RiteVM Component with Bluetooth Loader for mruby Bytecode}
\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/component_bluetooth.eps}
\caption{Component diagram of Bluetooth loader for mruby bytecode}
\label{fig:component_bluetooth}
\end{figure}
The proposed framework provides a RiteVM with a Bluetooth loader for mruby bytecode as a TECS component.
This component is an extension of the RiteVM component described in \cite{par:mrubyonTECS}.
It receives bytecodes via Bluetooth and manages the RiteVM configuration, such as generating mruby library bytecodes automatically.
This generated bytecode is prepared beforehand on the storage/ROM device and differs from the bytecode transferred with Bluetooth.

Figure \ref{fig:component_bluetooth} shows a component diagram of MrubyTask1 and RiteVMBluetooth1 {\it cell}s.
The MrubyTask1 {\it cell} is a componentized task of the RTOS (TOPPERS/HRP2 \cite{url:HRP2}, \cite{par:hr-tecs}).
The RiteVMBluetooth1 {\it cell} is the RiteVM component with the Bluetooth loader for mruby bytecode.
Bytecode on the host is transferred and received.
In this framework, ZMODEM \cite{par:zmodem} is used as the binary transfer protocol.

\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/control_flow.eps}
\caption{Process flow of Bluetooth loader for mruby bytecode}
\label{fig:control_flow}
\end{figure}

\begin{figure}[t]
\centering
\begin{lstlisting}
/* tRiteVMBluetooth.cdl */
celltype tRiteVMBluetooth1 {
    entry sTaskBody eMrubyBody;
    [optional] call sEventflag cEventflag[];
    [optional] call sSemaphore cSemaphore;
    attr {
      [omit]char_t *mrubyLib;
      char_t *irepLib = 
                    C_EXP("&$cell_global$_irep");
      uint32_t irepAppSize = 
                    C_EXP( BUFFER_SIZE );
      FLGPTN setptn;
    };
    var {
        mrb_state *mrb;
        mrbc_context *context;
        [size_is(irepAppSize)] uint8_t *irepApp;
    };
};
\end{lstlisting}
\caption{Celltype description for RiteVM with Bluetooth loader for mruby bytecode}
\label{celltype_mrubybluetooth}
\end{figure}

@@

\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/rotateReadyQueue.eps}
\caption{RiteVM scheduler design}
\label{fig:rotateReadyQueue}
\end{figure}

\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/cyclic_handler.eps}
\caption{Component diagram of RiteVM scheduler}
\label{fig:cyclic_handler}
\end{figure}

@@

composite tRiteVMScheduler {
    attr {
        ATR    attribute      = C_EXP("TA_NULL");
        RELTIM cyclicTime  = 1;
        RELTIM cyclicPhase = 1;
        PRI    priority;
    };
    cell tRiteVMSchedulerMain RiteVMSchedulerMain {
        priority = composite.priority;
    };
    cell tCyclicHandler CyclicHandler {
        ciBody      = RiteVMSchedulerMain.eiBody;
        attribute   = composite.attribute;
        cyclicTime  = composite.cyclicTime;
        cyclicPhase = composite.cyclicPhase;
    };
};
    \end{lstlisting}
\caption{Celltype description of RiteVM scheduler}
\label{celltype_cyclic_handler}
\end{figure}
\begin{figure}[t]
    \centering
    \begin{lstlisting}
cell tRiteVMScheduler RiteVMScheduler {
    attribute   = C_EXP("TA_STA");
    cyclicTime  = 1;
    cyclicPhase = 1;
    priority    =
        C_EXP("RITEVM_PRIORITY");
};
\end{lstlisting}
\caption{Build description of RiteVM scheduler}
\label{build_cyclic_handler}
\end{figure}

@@

Figure \ref{fig:cyclic_handler} shows a component diagram of the RiteVM scheduler.
The RiteVM scheduler consists of CyclicHandler and RiteVMSchedulerMain.
The CyclicHandler {\it cell} configures the periodic handler based on $\mu$ITRON.
Cyclic handlers based on $\mu$ITRON are described in the literature \cite{par:microITRON}.
The CyclicHandler {\it cell} has the attributes of the {\it cell}.
The RiteVMSchedulerMain {\it cell} processes the body of a periodic handler.
Note that {\it rotateReadyQueue} is implemented as the body.
Figure \ref{celltype_cyclic_handler} shows tRiteVMScheduler {\it celltype}, which is a {\it composite cell} consisting of two {\it cell}s.
The {\it call} port of RiteVMSchedulerMain is connected to the {\it entry} port of the Kernel {\it cell} ({\it tKernel.eiKernel}) to call kernel functions.
The attribute is used as the {\it rotateReadyQueue} arguments.

Figure \ref{build_cyclic_handler} shows the build description of the RiteVM scheduler.
The RiteVMScheduler {\it cell} has attributes to configure the scheduler such as attribute, cyclicTime, cyclicPhase, and priority.
In this case, the RiteVM scheduler is executed when it is generated, because the attribute is {\it TA\_STA}, which indicates that the periodic handler is in an operational state after creation.
Note that the scheduler executes every 1 msec.
RITEVM\_PRIORITY defines the priority of mruby tasks.
In the function of RiteVMSchedulerMain, {\it rotateReadyQueue} is implemented and the priority is passed as the argument.

\begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/Eventflag.eps}
\caption{Design of Eventflag using TECS (only differences are shown)}
\label{fig:Eventflag}
\end{figure}

@@

 \begin{figure}[t]
    \centering
    \includegraphics[width=6.5cm,clip]{figure/eval_synchronization.eps}
\caption{Synchronization of multiple RiteVM tasks}
\label{fig:eval_synchronization}
\end{figure}
